---
title: "Improving security in London: Evidence of a crime"
author: "Xuhang Guo"
date: "2021/1/11"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###library a few packages###
library(pacman)
p_load(broom,corrr,spatstat,car,ggplot2,sp,rgeos,maptools,GISTools,tmap,sf,geojson,geojsonio,tmaptools,tidyverse,raster,fpc,dbscan,here,dplyr,spData,spdep)
library(broom)

###########################
#####Cluster for Crime#####
###########################
#read the SHP file
london_map<-readOGR(here::here("data/gis-london/ESRI/London_Borough_Excluding_MHW.shp"))
london_map1 <- fortify(london_map) 
#join the GSS_CODE information
x <- london_map@data
xs <- data.frame(x,id=seq(0:32)-1) 
london_map_data <- join(london_map1, xs, type = "full")

#read the cluster data
Crimeborough<-read.csv(here::here("data/CrimeCluster.csv"))
#impute the missing value with mean value
Crimeborough$ViolenceAgainst[1]<-mean(Crimeborough$ViolenceAgainst,na.rm = T)
Crimeborough$SexualOffences[1]<-mean(Crimeborough$SexualOffences,na.rm = T)
Crimeborough$Robbery[1]<-mean(Crimeborough$Robbery,na.rm = T)
Crimeborough$Burglary[1]<-mean(Crimeborough$Burglary,na.rm = T)
Crimeborough$Theft[1]<-mean(Crimeborough$Theft,na.rm = T)
Crimeborough$Fraud[1]<-mean(Crimeborough$Fraud,na.rm = T)
Crimeborough$CriminalDamage[1]<-mean(Crimeborough$CriminalDamage,na.rm = T)
Crimeborough$Drugs[1]<-mean(Crimeborough$Drugs,na.rm = T)
Crimeborough$Other[1]<-mean(Crimeborough$Other,na.rm = T)

#do k-means cluster
library(cluster)
set.seed(123)
Crimecluster<-kmeans(Crimeborough[,4:12],3)
#get the cluster class
Crimeborough$cluster<-Crimecluster$cluster

#get the draw value
Crimeborough_new<-Crimeborough[,c(1,2,13)]
#rename 
names(Crimeborough_new)<-c("GSS_CODE","code2","Type")

#join the finial data
londonCrime_data <- join(london_map_data, Crimeborough_new, type="full",by="GSS_CODE")
londonCrime_data$Type[londonCrime_data$Type==3]<-"High"
londonCrime_data$Type[londonCrime_data$Type==2]<-"Median"
londonCrime_data$Type[londonCrime_data$Type==1]<-"Low"

#manual set the two type col
rhg_cols1 <- c("#9999FF","#66CCFF","#FFCCCC")

#add the mark
#get the ward center coordinate
#ddply() function in plyr,group by ward
midpos <- function(AD1){mean(range(AD1,na.rm=TRUE))} 
centres <- ddply(londonCrime_data,.(code2),colwise(midpos,.(long,lat)))
centres1<-centres
centres1$code2<-as.numeric(centres1$code2)

#manual adjust the coordinate
centres1$lat[centres1$code2==2]<-centres1$lat[centres1$code2==2]-1000
centres1$lat[centres1$code2==18]<-centres1$lat[centres1$code2==18]+2000
centres1$long[centres1$code2==13]<-centres1$long[centres1$code2==13]-500
centres1$long[centres1$code2==20]<-centres1$long[centres1$code2==20]+500
centres1$lat[centres1$code2==20]<-centres1$lat[centres1$code2==20]-1000
centres1$lat[centres1$code2==30]<-centres1$lat[centres1$code2==30]+500


#draw the plot
Crimeclustermap<-ggplot(londonCrime_data, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = Type),colour="grey30",size=0.05) +
  geom_text(data=centres1,aes(x=long,y=lat,label=code2),size=3,col="black",fontface = "bold")+
  scale_fill_manual(values=rhg_cols1)+  
  guides(fill=guide_legend(title='Type'))+  ##legend name as Type
  theme(                            
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
Crimeclustermap
```{r ClusterCrimemap, echo=FALSE}
plot(Crimeclustermap)
```

####################################
#####Cluster of personal income#####
####################################
#read the SHP file
london_map<-readOGR(here::here("data/gis-london/ESRI/London_Borough_Excluding_MHW.shp"))
london_map1 <- fortify(london_map) 
#join the GSS_CODE information
x <- london_map@data
xs <- data.frame(x,id=seq(0:32)-1) 
london_map_data <- join(london_map1, xs, type = "full")

#read the cluster data
brough<-read.csv(here::here("data/cluster.csv"))
#impute the missing value with mean value
brough$Working_Households[1]<-mean(brough$Working_Households,na.rm = T)


#do k-means cluster
library(cluster)
set.seed(123)
cluster<-kmeans(brough[,4:6],3)
#get the cluster class
brough$cluster<-cluster$cluster

#get the draw value
brough_new<-brough[,c(1,2,7)]
#rename 
names(brough_new)<-c("GSS_CODE","code2","Type")

#join the finial data
london_data <- join(london_map_data, brough_new, type="full",by="GSS_CODE")
london_data$Type[london_data$Type==3]<-"Rich"
london_data$Type[london_data$Type==2]<-"Middle"
london_data$Type[london_data$Type==1]<-"Poor"

#manual set the two type col
rhg_cols1 <- c("#9966CC","#6699FF","#FF99CC")

#add the mark
#get the ward center coordinate
#ddply() function in plyr,group by ward
midpos <- function(AD1){mean(range(AD1,na.rm=TRUE))} 
centres <- ddply(london_data,.(code2),colwise(midpos,.(long,lat)))
centres1<-centres
centres1$code2<-as.numeric(centres1$code2)

#manual adjust the coordinate
centres1$lat[centres1$code2==2]<-centres1$lat[centres1$code2==2]-1000
centres1$lat[centres1$code2==18]<-centres1$lat[centres1$code2==18]+2000
centres1$long[centres1$code2==13]<-centres1$long[centres1$code2==13]-500
centres1$long[centres1$code2==20]<-centres1$long[centres1$code2==20]+500
centres1$lat[centres1$code2==20]<-centres1$lat[centres1$code2==20]-1000
centres1$lat[centres1$code2==30]<-centres1$lat[centres1$code2==30]+500

#draw the plot
clusterincomemap<-ggplot(london_data, aes(x = long, y = lat)) +
  geom_polygon(aes(group = group, fill = Type),colour="grey30",size=0.05) +
  geom_text(data=centres1,aes(x=long,y=lat,label=code2),size=3,col="black",fontface = "bold")+
  scale_fill_manual(values=rhg_cols1)+  
  guides(fill=guide_legend(title='Type'))+  ##legend name as Type
  theme(                            
    panel.grid = element_blank(),
    panel.background = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  )
clusterincomemap
```{r clusterincomemap, echo=FALSE}
plot(clusterincomemap)
```

###############################
#####The map of Populaiton#####
###############################
#read the shapefile of Borough
LondonBoroughs<-st_read(here::here("data/gis-london/ESRI/London_Borough_Excluding_MHW.shp"))
#read the data
st_crs(LondonBoroughs)
#Visualization
tmap_mode("view")
#read the csv
LondonP<-read_csv(here::here("data/Regressiondata.csv"))
LondonPop<-LondonP%>%
  dplyr::select(Population,Code,Borough)
#merge boundaries and data
LondonBorPop <- LondonBoroughs%>%
  left_join(.,
            LondonPop, 
            by = c("GSS_CODE" = "Code"))
#let's map our dependent variable to see if the join has worked:
tmap_mode("view")
qtm(LondonBorPop, 
    fill = "Population", 
    borders = "black", alpha=0.5, 
    fill.palette = "RdGy")



###################
#####Residuals#####
###################
###Map of Crime###
#Visualization
tmap_mode("view")
#read the data
st_crs(LondonBoroughs)
#read the csv
Crime<-read_csv(here::here("data/Regressiondata.csv"))%>%
  dplyr::select(Crime)
#read the csv
LondonCrime<-read_csv(here::here("data/Crime_counts.csv"),
                      na = c("", "NA", "n/a"), 
                      locale = locale(encoding = 'Latin1'), 
                      col_names = TRUE)
#breaks
breaks = c(0,10000,20000,30000,40000,50000,60000,70000)
#map the Number of Crime in 2016
London_Crime = left_join(LondonBoroughs,LondonCrime, 
                         by = c("GSS_CODE" = "Code"))
Crime2011<-tm_shape(London_Crime) + 
  tm_polygons(col = "Crime_2011", palette = "PRGn",breaks=breaks) + 
  tm_facets(nrow = 1, sync = TRUE)
Crime2011

#lm
Model <- read_csv(here::here("data/Regressiondata.csv"))%>%
  lm(Crime ~ LLW + Workless + PublicTransportAccessibility+Population, data=.)
#extract the residuals
res_Model <- residuals(Model)
#prediction
fitted_Model <- fitted(Model)  
# also add them to the shapelayer
London_Crime <- London_Crime %>%
  mutate(res_Model)
LonCrime<-London_Crime[-1,]%>%
  add_column(fitted_Model,res_Model)
#qtm
tm_shape(LonCrime) +
  tm_polygons("Crime_2011",palette ="-RdBu",alpha = 0.8) +
  tm_shape(LonCrime) + tm_dots("res_Model",palette="PRGn",size=0.1)



#########################
#####Moran's I-Crime#####
#########################

#read the data
LonC<-read_csv(here::here("data/Regressiondata.csv"))%>%
  dplyr::select(Crime,Code,Borough)
#join
LondonC<-LondonBoroughs%>%
  left_join(.,LonC,by = c("GSS_CODE" = "Code"))
#supplement
LondonC$Crime[33]<-814626
#calculate the centroids of all Wards in London
coordsLonCrime<- LondonC%>%
  st_centroid()%>%
  st_geometry()
plot(coordsW)
#generate a spatial weights matrix
LonC_nb <- LondonC %>%
  poly2nb(., queen=T)
#plot them
plot(LonC_nb, st_geometry(coordsLonCrime), col="red")
#create a spatial weights matrix object from these weights
LC.queens_weight <- LonC_nb %>%
  nb2listw(., style="C")
#Queen neighbours
QueenCrime<- LondonC%>%
  st_drop_geometry()%>%
  dplyr::select(Crime)%>%
  pull()%>%
  moran.test(., LC.queens_weight)%>%
  tidy()
QueenCrime



#########################
#####Moran's I-LLW#####
#########################
#read the data
LonLLW<-read_csv(here::here("data/Regressiondata.csv"))%>%
  dplyr::select(LLW,Code,Borough)
#join
LondonLLW<-LondonBoroughs%>%
  left_join(.,LonLLW,by = c("GSS_CODE" = "Code"))
#read
LondonLLW$LLW[33]<-15000
#calculate the centroids of all Wards in London
coordsLLW<- LondonLLW%>%
  st_centroid()%>%
  st_geometry()
plot(coordsLLW)
#generate a spatial weights matrix
LonLLW_nb <- LondonLLW %>%
  poly2nb(., queen=T)
#plot them
plot(LonLLW_nb, st_geometry(coordsLLW), col="red")
#create a spatial weights matrix object from these weights
LLLW.queens_weight <- LonLLW_nb %>%
  nb2listw(., style="C")
#Queen neighbours
QueenLLW<- LondonLLW %>%
  st_drop_geometry()%>%
  dplyr::select(LLW)%>%
  pull()%>%
  moran.test(., LLLW.queens_weight)%>%
  tidy()
QueenLLW



################################
#####Moran's I-Worklessness#####
################################
#read the data
LonW<-read_csv(here::here("data/Regressiondata.csv"))%>%
  dplyr::select(Workless,Code,Borough)
#join
LondonW<-LondonBoroughs%>%
  left_join(.,LonW,by = c("GSS_CODE" = "Code"))
#read
LondonW$Workless[33]<-5
#calculate the centroids of all Wards in London
coordsW<- LondonW%>%
  st_centroid()%>%
  st_geometry()
plot(coordsW)
#generate a spatial weights matrix
LonW_nb <- LondonW %>%
  poly2nb(., queen=T)
#plot them
plot(LonW_nb, st_geometry(coordsW), col="red")
#create a spatial weights matrix object from these weights
LW.queens_weight <- LonW_nb %>%
  nb2listw(., style="C")
#Queen neighbours
QueenW<- LondonW %>%
  st_drop_geometry()%>%
  dplyr::select(Workless)%>%
  pull()%>%
  moran.test(., LW.queens_weight)%>%
  tidy()
QueenW



################################################
#####MORAN's I-PublicTransportAccessibility#####
################################################
#read the data
LonTransport<-read_csv(here::here("data/Regressiondata.csv"))%>%
  dplyr::select(PublicTransportAccessibility,Code,Borough)
LondonT<-LondonBoroughs%>%
  left_join(.,LonTransport,by = c("GSS_CODE" = "Code"))
#read
LondonT$PublicTransportAccessibility[33]<-3
#calculate the centroids of all Wards in London
coordsT <- LondonT%>%
  st_centroid()%>%
  st_geometry()
plot(coordsT)
#generate a spatial weights matrix
LonT_nb <- LondonT %>%
  poly2nb(., queen=T)
#plot them
plot(LonT_nb, st_geometry(coordsT), col="red")
#create a spatial weights matrix object from these weights
LT.queens_weight <- LonT_nb %>%
  nb2listw(., style="C")
#Queen neighbours
QueenT<- LondonT %>%
  st_drop_geometry()%>%
  dplyr::select(PublicTransportAccessibility)%>%
  pull()%>%
  moran.test(., LT.queens_weight)%>%
  tidy()
QueenT



##############################
#####MORAN's I-Population#####
##############################
#read
LonBorPop$Population[33]<-7338
#calculate the centroids of all Wards in London
coordsPop <- LonBorPop%>%
  st_centroid()%>%
  st_geometry()
plot(coordsPop)
#generate a spatial weights matrix
LonPop_nb <- LonBorPop %>%
  poly2nb(., queen=T)
#plot them
plot(LonPop_nb, st_geometry(coordsPop), col="red")
#create a spatial weights matrix object from these weights
LPop.queens_weight <- LonPop_nb %>%
  nb2listw(., style="C")
#Queen neighbours
QueenPop<- LonBorPop %>%
  st_drop_geometry()%>%
  dplyr::select(Population)%>%
  pull()%>%
  moran.test(., LPop.queens_weight)%>%
  tidy()
QueenPop


#############
#####OLS#####
#############
#OLS_Model
OLS<-read_csv(here::here("data/Regressiondata.csv"))
Model_OLS<-OLS%>%
  lm(Crime ~ LLW+Workless+PublicTransportAccessibility+Population,data=.)
#show the summary of those outputs
summary(Model_OLS)


##################
#####LM-tests#####
##################
#lm
Model1<- read_csv(here::here("data/Regressiondata.csv"))%>%
  lm(Crime ~ LLW+ Workless + PublicTransportAccessibility + Population, data=.)
#test
lm.LMtests(Model1, wm, test = c("LMerr","LMlag","RLMerr","RLMlag","SARMA"))


###################################################
#####Geographically Weighted Regression Models#####
###################################################
#read the packages for GWR
library(spgwr)

#link
LonCrime = left_join(LonCrime,data, 
                         by = c("GSS_CODE" = "Code"))
LonCrime<-LonCrime[-32,]

#change the sf to sp
st_crs(LonCrime) = 27700
LonCrimeSP <- LonCrime %>%
  as(., "Spatial")
st_crs(coordsLonCrime) = 27700
coordsLonCrimeSP <- coordsLonCrime %>%
  as(., "Spatial")
#view
coordsLonCrimeSP

#calculate kernel bandwidth
GWRbandwidth <- gwr.sel(Crime ~ LLW + 
                          Workless + 
                          PublicTransportAccessibility + 
                          Population, 
                        data = LonCrimeSP, 
                        coords=coordsLonCrimeSP,
                        adapt=T)
#run the gwr model
gwr.model = gwr(Crime ~ LLW + 
                  Workless + 
                  PublicTransportAccessibility + 
                  Population,
                data = LonCrimeSP, 
                coords=coordsLonCrimeSP,
                adapt=GWRbandwidth, 
                hatmatrix=TRUE, 
                se.fit=TRUE)
#print the results of the model
gwr.model
#show the name of results
results <- as.data.frame(gwr.model$SDF)
names(results)
#attach coefficients to original SF
LonCrime2 <- LonCrime2 %>%
  mutate(coefLLW = results$LLW,
         coefWorkless = results$Workless,
         coefPTA = results$PublicTransportAccessibility,
         coefPopulation = results$Population,
         GWRLocalR2=results$localR2)


##MAP (LLW)
#plot of LLW
tmap_mode("view")
coefLLW<-tm_shape(LonCrime2) +
  tm_polygons(col = "coefLLW", 
              palette = "RdBu", 
              alpha = 0.5)
coefLLW
#run the significance test
sigTest = abs(gwr.model$SDF$"Workless")-2 * gwr.model$SDF$"Workless_se"
#store significance results
LonCrime2 <- LonCrime2 %>%
  mutate(GWRLLW = sigTest)
#map (LLW)
GWRLLW<-tm_shape(LonCrime2) +
  tm_polygons(col = "GWRLLW", 
              palette = "RdBu",
              alpha = 0.5)
GWRLLW

###Map(coefWorkless)
#plot of Population
tmap_mode("view")
coefWorkless<-tm_shape(LonCrime2) +
  tm_polygons(col ="coefWorkless", 
              palette = "RdBu", 
              alpha = 0.5)
coefWorkless
#run the significance test
sigTest2 = abs(gwr.model$SDF$"LLW")-2 * gwr.model$SDF$"LLW_se"
#store significance results
LonCrime2 <- LonCrime2 %>%
  mutate(GWRWorkless = sigTest2)
#map (GWRworkless)
GWRWorkless<-tm_shape(LonCrime2) +
  tm_polygons(col = "GWRWorkless", 
              palette = "RdBu",
              alpha = 0.5)
GWRWorkless

###Map(coefPopulation)
#plot of Population
tmap_mode("view")
coefPopulation<-tm_shape(LonCrime2) +
  tm_polygons(col ="coefPopulation", 
              palette = "PiYG", 
              alpha = 0.5)
coefPopulation
#run the significance test (populaiton)
sigTest3= abs(gwr.model$SDF$"PublicTransportAccessibility")-2 * gwr.model$SDF$"PublicTransportAccessibility_se"
#store significance results
LonCrime2 <- LonCrime2 %>%
  mutate(GWRPopulation = sigTest3)
#map (coefPopulation)
GWRPopulation<-tm_shape(LonCrime2) +
  tm_polygons(col = "GWRPopulation", 
              palette = "PiYG",
              alpha = 0.5)
GWRPopulation

###Map(coefPTA)
#plot of Population
tmap_mode("view")
coefPTA<-tm_shape(LonCrime2) +
  tm_polygons(col ="coefPTA", 
              palette = "PiYG", 
              alpha = 0.5)
coefPTA
#run the significance test
sigTest4 = abs(gwr.model$SDF$"Population")-2 * gwr.model$SDF$"Population_se"
#store significance results
LonCrime2 <- LonCrime2 %>%
  mutate(GWRPTA = sigTest4)
#map (GWRPTA)
GWRPTA<-tm_shape(LonCrime2) +
  tm_polygons(col = "GWRPTA", 
              palette = "PiYG",
              alpha = 0.5)
GWRPTA

###Map(LocalR2)
#plot of Population
tmap_mode("view")
GWRLocalR2<-tm_shape(LonCrime2) +
  tm_polygons(col ="GWRLocalR2", 
              palette = "PRGn", 
              alpha = 0.5)
GWRLocalR2